Hydraulically-vulnerable trees are buffered by deep-water access in a tropical forest community

### 2020-10-24 old_ms_sections.Rmd
# moved in discussion on Chitra-Tarak 2018

>>>>

The model in CT2018 were not corroborated with such data as existing methods were inadequate to extract water bound to the saprolite found in their dry forest study site (Jean Riotte, pers. comm.). The model of below-ground water-availability in this study (ELM-FATES) differs from the conceptual water balance model used by CT2018 and was calibrated with data on long-term soil moisture dynamics at a point location (0-0.15m) and plot-wide measurements by depth (0.15, 0.4 and 1 m), as well as, evapotranspiration and stream discharge. The model in CT2018 was calibrated only on stream discharge and water table levels.
